### 2024-08-10 paper.tex
start talking about centralizer

>>>>

\section{Finding a centralizer}
For nilpotent \(X\) in Jordan form and \(a\) in `normalized' form (i.e., with at most one nonzero element, which is a one), we will find the centralizer of \(A_{X, a, b}\) in 
\[\{(A, I) : A \in \gl_m\} \subseteq \gl_{m + n}.\]
Note that an element of the form \((A, I)\) commutes with \(A_{X, a, b}\) if and only if \(A\) commutes with \(X\), and \(aA = a\), and \(Ab = b\).
So, we just have to find 
\[\{A \in \gl_m : AX = XA, aA = a, Ab = b\}.\]
We begin by finding 
\[\{A \in \gl_m : AX = XA\}.\]
We write the shape of \(X\) as \(\lambda = (\lambda_1, ..., \lambda_k)\), so that 
\[X = \begin{pmatrix}
    J_{\lambda_1} & \\
    & \ddots \\
    & & J_{\lambda_k}
\end{pmatrix}.\]
Then we write \(A\) as the block matrix
\[A =: \begin{pmatrix}
    A_{11} & \cdots & A_{1k}\\
    \vdots & & \vdots\\
    A_{k1} & \cdots & A_{kk}
\end{pmatrix},\]
where \(A_{ij}\) is a block of size \(\lambda_i \times \lambda_j\).
We have 
\[XA = \begin{pmatrix}
    J_{\lambda_1}A_{11} & \cdots & J_{\lambda_1}A_{1k}\\
    \vdots & & \vdots\\
    J_{\lambda_k}A_{k1} & \cdots & J_{\lambda_k}A_{kk}
\end{pmatrix}, \textrm{ and } AX = \begin{pmatrix}
    A_{11} J_{\lambda_1} & \cdots & A_{1k} J_{\lambda_k}\\
    \vdots & & \vdots\\
    A_{k1} J_{\lambda_1} & \cdots & A_{kk} J_{\lambda_k}
\end{pmatrix}.\]
So, the constraint that \(XA = AX\) is simply saying that 
\[\forall i,j. \; J_{\lambda_i} A_{ij} = A_{ij} J_{\lambda_j}.\]
It's easy to see that left multiplication by \(J_{\lambda_i}\) is just a down-shift by one, and right multiplication by \(J_{\lambda_j}\) is a left-shift by one.
This means that \(A_{ij}\) is constrained to be a ``lower-left-Toeplitz'' matrix; one of the form
